Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-16 paper/structureScene.tex
Remove addressed comments

Despite the differences, ecoacoustics and acoustic scene classification (ASC) task both raise the following question: how can we efficiently and effectively process a large amount of audio data using representations that are compact, generic in their design, and flexible in their use?
The work described in this paper attempts to answer this question by demonstrating the usefulness of two concepts for environmental audio processing: 1) application of the wavelet scattering transform to extract discriminative features and 2) large time-scale modeling of the acoustic scene based on unsupervised clustering of each acoustic scene, allowing us to focus the scene description on a few salient sound objects that carry most of the semantic information. %\ja{Technically, the 1st concept has already been demonstrated in previous papers. Do we really want to claim this here?} ML narrowed the scope

@@

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE 2013 private dataset of acoustic scene classification. Algorithms above the horizontal line participated to the DCASE challenge. The algorithm marked with $^*$ considered only the public dataset. \label{tab:dcase} \ml{need to define RQA ILD LDA or remove table ?} %\ja{What are the initials OE, ELF, etc. for? Do we need them?}
}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\hline
\cite{olivetti2013wonder} & 17 & compression distance, random forests \\
\cite{elizalde2013vector} & 55 & i-vector, LDA \\
\cite{krijnders2013tone} & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} & 60 & unsupervised learning over mel spectra, SVMs \\
\cite{nogueira2013sound} & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} & 69 & mel spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} & 72 & MFCCs, tree baggers \\
\cite{roma2013} & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

@@

As discussed in Section \ref{sec:soa}, results in sound perception suggest the appropriateness of source-driven representations of auditory scenes for predicting high-level properties. As the detection of events is still an open problem \cite{7100934}, we consider in this paper a generic quantization scheme in order to identify and represent time intervals of the scene that are coherent, thus likely to be dominated by a given source of interest. \ja{This last sentence is a bit hard to parse. Are we segmenting the time-series and identifying coherent regions?} \ml{better ?}

@@

The performance of the temporal scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (ASSR) and in a supervised setting (ASC). \ja{The \emph{ob} approaches are not really assessed for ASC, though.} \ml{well, we say that this does not work well, no ?}

@@

Logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale. \ja{Isn't this why we also standardize the coefficients?} \vl{No, standardization does not affect skewness, unlike log compression}
This transformation improves the discriminative power of the SVMs trained on scattering coefficients, regardless of the chosen temporal integration strategy (early or late) and the inner product kernel (linear or Gaussian RBF).
Again, this is in accordance with our previous findings on acoustic scene similarity retrieval, which are reported in Figure \ref{fig:ASS_2}.

\begin{table}
\begin{center}
\caption{
\label{table:dcase2013}
Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.
\ja{The relationship between linear and RBF is inverted for the \emph{early} integration scheme compared to \emph{late}. Is this correct?}
}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
\emph{early}, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
\emph{early}, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
\emph{late}, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
\emph{late}, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\end{center}
\end{table}

>>>>

Despite the differences, ecoacoustics and acoustic scene classification (ASC) task both raise the following question: how can we efficiently and effectively process a large amount of audio data using representations that are compact, generic in their design, and flexible in their use?
The work described in this paper attempts to answer this question by demonstrating the usefulness of two concepts for environmental audio processing: 1) application of the wavelet scattering transform to extract discriminative features and 2) large time-scale modeling of the acoustic scene based on unsupervised clustering of each acoustic scene, allowing us to focus the scene description on a few salient sound objects that carry most of the semantic information.

@@

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE 2013 private dataset of acoustic scene classification. Algorithms above the horizontal line participated to the DCASE challenge. The algorithm marked with $^*$ considered only the public dataset. \label{tab:dcase} \ml{need to define RQA ILD LDA or remove table ?} 
}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\hline
\cite{olivetti2013wonder} & 17 & compression distance, random forests \\
\cite{elizalde2013vector} & 55 & i-vector, LDA \\
\cite{krijnders2013tone} & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} & 60 & unsupervised learning over mel spectra, SVMs \\
\cite{nogueira2013sound} & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} & 69 & mel spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} & 72 & MFCCs, tree baggers \\
\cite{roma2013} & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

@@

As discussed in Section \ref{sec:soa}, results in sound perception suggest the appropriateness of source-driven representations of auditory scenes for predicting high-level properties. As the detection of events is still an open problem \cite{7100934}, we consider in this paper a generic quantization scheme in order to identify and represent time intervals of the scene that are coherent, thus likely to be dominated by a given source of interest.

@@

The performance of the temporal scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (ASSR) and in a supervised setting (ASC).

@@

Logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale. This transformation improves the discriminative power of the SVMs trained on scattering coefficients, regardless of the chosen temporal integration strategy (early or late) and the inner product kernel (linear or Gaussian RBF).
Again, this is in accordance with our previous findings on acoustic scene similarity retrieval, which are reported in Figure \ref{fig:ASS_2}.

\begin{table}
\begin{center}
\caption{
\label{table:dcase2013}
Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.
}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
\emph{early}, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
\emph{early}, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
\emph{late}, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
\emph{late}, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\end{center}
\end{table}
